---
title: "DMTM Project FA22"
output: html_notebook
author: "Benjamin Dinal, David Schindler"
---

# Library & Data Loading; General Statistics & Summary

```{r}
library(topicdoc)
library(topicmodels)
library(tidyverse)
library(tidytext)
library(dplyr)
library(ggplot2)
library(mosaic)
library(RColorBrewer)
library(wordcloud)
library(reshape2)
```


```{r}
DL <- read.csv("DisneylandReviews.csv")
DLReview <- (select(DL, Review_ID, Rating, Year, Year_Month, Reviewer_Continent, Reviewer_Country, Review_Text, Branch))
```

This dataset consists of over 40000 reviews from TripAdvisor for Disneyland Paris, Hong Kong, and California. The dataset was downloaded via Kaggle, and cleaned client-side.

```{r}
head(DLReview)
```

```{r}
DLReview %>%
  count(Branch, sort = TRUE)

DLReview %>%
  count(Rating)

DLReview %>%
  count(Review_ID, sort = TRUE)

DLReview %>%
  count(Reviewer_Continent)
```

Most Reviewers are from North America, having 15826 reviews. Europe has 11731, and Asia has 6708.

18200 reviews are for Disneyland CA, 12693 are for Disneyland Paris, and 9138 are for Disneyland HK.

More than half of the entire data set consists of 5 Star reviews.

# Data Manipulation

We are going to partition the data into 3 regions: North America and South America will combine, Europe and Africa will combine, and Oceania and Asia will combine. 

```{r}
DLR_Amer <- DLReview %>% 
  filter((Reviewer_Continent == "North America")|(Reviewer_Continent=="South America")) %>% 
  unnest_tokens(word, Review_Text) %>%
  anti_join(stop_words)


head(DLR_Amer)
```

```{r}
DLR_AfEu <- DLReview %>% 
  filter((Reviewer_Continent == "Africa")|(Reviewer_Continent=="Europe")) %>% 
  unnest_tokens(word, Review_Text) %>%
  anti_join(stop_words)


head(DLR_AfEu)
```

```{r}
DLR_AsOc <- DLReview %>% 
  filter((Reviewer_Continent == "Asia")|(Reviewer_Continent=="Oceania")) %>% 
  unnest_tokens(word, Review_Text) %>%
  anti_join(stop_words)


head(DLR_AsOc)
```

# Sentiment Analysis on All Three Disneyland Parks Partitioned by Region
## Region - The Americas

Now we will perform Sentiment Analysis using the "Bing" lexicon on each region's reviews. First, this will be a Sentiment Analysis of all three Disneyland Parks combined (HK, CA, PR)

```{r}
DLR_Amer %>%
  inner_join(get_sentiments("bing")) %>%
  count(Review_ID, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  ggplot() + 
  geom_bar(aes(x = reorder(Review_ID, sentiment),
               y = sentiment), 
           stat = "identity") + 
  coord_flip() + 
  labs(x = "", 
       title = "Sentiment Analysis of Reviews in the Americas using Bing Lexicon",
       subtitle = "Sorted by Reviewer ID")
```

While difficult to read, this Sentiment Analysis shows that an overwhelming majority of Reviewers had positive things to say. This is beneficial because it aligns with the Stars Ratings - more than half of the data-set is 5 star reviews, and more than half of this sample contains a positive sentiment.

```{r}
DLR_Amer %>%
  inner_join(get_sentiments("bing")) %>%
  count(Year, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  ggplot() + 
  geom_bar(aes(x = reorder(Year, sentiment),
               y = sentiment), 
           stat = "identity") + 
  coord_flip() + 
  labs(x = "", 
       title = "Sentiment Analysis of Reviews in the Americas using Bing Lexicon",
       subtitle = "Sorted by Year")

```

In this sentiment analysis, we see that 2015 had an overwhelmingly high sentiment score. This can be attributed to the fact that, for the America's, Disneyland California celebrated it's 60th Year Anniversary. However, if we were to exclude Disneyland California, 2017's sentiment score is the highest.

##Sentimental analysis with *nrc* lexicon

```{r}
DLR_Amer_lo_words <- DLR_Amer%>%
  inner_join(get_sentiments("nrc")) %>%
  group_by(sentiment, word) %>%
  count(mycount = n()) %>%
  distinct() %>%
  filter(sentiment %in%
  c("anger", "fear", "anticipation", "trust", "surprise", "sadness", "joy", "disgust"))


head(DLR_Amer_lo_words)
```

```{r}

ggplot(DLR_Amer_lo_words, aes(x=sentiment, y=n)) +
  geom_bar(stat="identity", width=0.5)
```


```{r}
DLR_Amer_wordcloud_sentiment <- DLR_Amer %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word~sentiment, value.var ="n", fill=0) %>%
  comparison.cloud(colors = c("blue","red"), max.words = 50)


```

```{r}
DLR_Amer_Cali <- DLReview %>% 
  filter(((Reviewer_Continent == "North America")|(Reviewer_Continent=="South America"))&(Branch=="Disneyland_California")) %>% 
  unnest_tokens(word, Review_Text) %>%
  anti_join(stop_words)


head(DLR_Amer_Cali)
```
```{r}
DLR_Amer_Cali_wordcloud_sentiment <- DLR_Amer_Cali %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word~sentiment, value.var ="n", fill=0) %>%
  comparison.cloud(colors = c("blue","red"), max.words = 50)


```


```{r}
DLR_Amer_HK <- DLReview %>% 
  filter(((Reviewer_Continent == "North America")|(Reviewer_Continent=="South America"))&(Branch=="Disneyland_HongKong")) %>% 
  unnest_tokens(word, Review_Text) %>%
  anti_join(stop_words)


head(DLR_Amer_HK)
```

```{r}
DLR_Amer_HK_wordcloud_sentiment <- DLR_Amer_HK %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word~sentiment, value.var ="n", fill=0) %>%
  comparison.cloud(colors = c("blue","red"), max.words = 50)


```

```{r}
DLR_Amer_Paris <- DLReview %>% 
  filter(((Reviewer_Continent == "North America")|(Reviewer_Continent=="South America"))&(Branch=="Disneyland_Paris")) %>% 
  unnest_tokens(word, Review_Text) %>%
  anti_join(stop_words)


head(DLR_Amer_Paris)
```

```{r}
DLR_Amer_Paris_wordcloud_sentiment <- DLR_Amer_Paris %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word~sentiment, value.var ="n", fill=0) %>%
  comparison.cloud(colors = c("blue","red"), max.words = 50)


```



## Region: Euorpe and Africa

```{r}
DLR_AfEu %>%
  inner_join(get_sentiments("bing")) %>%
  count(Review_ID, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  ggplot() + 
  geom_bar(aes(x = reorder(Review_ID, sentiment),
               y = sentiment), 
           stat = "identity") + 
  coord_flip() + 
  labs(x = "", 
       title = "Sentiment Analysis of Reviews in the Eurafrica using Bing Lexicon",
       subtitle = "Sorted by Reviewer ID")
```



```{r}
DLR_AfEu %>%
  inner_join(get_sentiments("bing")) %>%
  count(Year, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  ggplot() + 
  geom_bar(aes(x = reorder(Year, sentiment),
               y = sentiment), 
           stat = "identity") + 
  coord_flip() + 
  labs(x = "", 
       title = "Sentiment Analysis of Reviews in the Eurafrica using Bing Lexicon",
       subtitle = "Sorted by Year")

```

```{r}
DLR_AfEu_lo_words <- DLR_AfEu%>%
  inner_join(get_sentiments("nrc")) %>%
  group_by(sentiment, word) %>%
  count(mycount = n()) %>%
  distinct() %>%
  filter(sentiment %in%
  c("anger", "fear", "anticipation", "trust", "surprise", "sadness", "joy", "disgust"))


head(DLR_AfEu_lo_words)
```

```{r}
ggplot(DLR_AfEu_lo_words, aes(x=sentiment, y=n)) +
  geom_bar(stat="identity", width=0.5)
```

```{r}
DLR_AfEu_wordcloud_sentiment <- DLR_AfEu %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word~sentiment, value.var ="n", fill=0) %>%
  comparison.cloud(colors = c("blue","red"), max.words = 40)


```



## Region: Asia and Oceania

```{r}
DLR_AsOc %>%
  inner_join(get_sentiments("bing")) %>%
  count(Review_ID, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  ggplot() + 
  geom_bar(aes(x = reorder(Review_ID, sentiment),
               y = sentiment), 
           stat = "identity") + 
  coord_flip() + 
  labs(x = "", 
       title = "Sentiment Analysis of Reviews in the Asia using Bing Lexicon",
       subtitle = "Sorted by Reviewer ID")
```



```{r}
DLR_AsOc %>%
  inner_join(get_sentiments("bing")) %>%
  count(Year, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  ggplot() + 
  geom_bar(aes(x = reorder(Year, sentiment),
               y = sentiment), 
           stat = "identity", fill="#393E8F", color="#F3CC64") + 
  coord_flip() + 
  labs(x = "", 
       title = "Sentiment Analysis of Reviews in the Asia using Bing Lexicon",
       subtitle = "Sorted by Year")

```


```{r}
DLR_AsOc_lo_words <- DLR_AsOc%>%
  inner_join(get_sentiments("nrc")) %>%
  group_by(sentiment, word) %>%
  count(mycount = n()) %>%
  distinct() %>%
  filter(sentiment %in%
  c("anger", "fear", "anticipation", "trust", "surprise", "sadness", "joy", "disgust"))


head(DLR_AsOc_lo_words)
```
```{r}
ggplot(DLR_AsOc_lo_words, aes(x=sentiment, y=n)) +
  geom_bar(stat="identity", width=0.5)
```

```{r}
DLR_AsOc_wordcloud_sentiment <- DLR_AsOc %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word~sentiment, value.var ="n", fill=0) %>%
  comparison.cloud(colors = c("blue","red"), max.words = 50)


```
